\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Conclusions

\subsection{ICANN and TLD Registrars}
The Internet Corporation for Assigned Names and Numbers (ICANN) is the organization responsible for the management of domain name system.
In 2009, ICANN started to accept applications for internationalized country code top-level domains (IDN ccTLDs).
The first IDN ccTLD was added to DNS root zone in 2010~\cite{mac2010}.
ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
They may reject applications for IDN ccTLDs if there exists an existing TLD that looks similar to the one being petitioned for.
The detailed checking process is defined in their ``Final Implementation Plan for IDN ccTLD Fast Track Process''~\cite{icann2013}.

Most second level registrars do not have a explicit public policy to prevent the registration of homograph domains.
Only a few have implemented restrictions to eliminate this potential risk.
For instance, \texttt{.cn}, \texttt{.biz}, \texttt{.hk}, and all Chinese TLDs will simultaneously activate both traditional and simplified Chinese IDNs once one of them is registered.

@@

\begin{table*}[b!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{IDNs} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

\section{Conclusions}
TODO
- Conclusions of our work
- Possible future work
- TLDs
- Hard to balance (rendering idn useless vs preventing the attack)

>>>>

\subsection{ICANN and TLD Registrars}
The Internet Corporation for Assigned Names and Numbers (ICANN) is the organization responsible for the management of domain name system.
In 2009, ICANN started to accept applications for internationalized country code top-level domains (IDN ccTLDs).
The first IDN ccTLD was added to DNS root zone in 2010~\cite{mac2010}.
ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
They may reject applications for IDN ccTLDs if there already exists a TLD that looks similar to the one being petitioned for.
The detailed checking process is defined in their ``Final Implementation Plan for IDN ccTLD Fast Track Process''~\cite{icann2013}.

Most second level registrars do not have an explicit public policy to prevent the registration of homograph domains.
Only a few have implemented restrictions to eliminate this potential risk.
For instance, \texttt{.cn}, \texttt{.biz}, \texttt{.hk}, and all Chinese TLDs will simultaneously activate both traditional and simplified Chinese IDNs once one of them is registered.

@@

\begin{table*}[b!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

\section{Conclusions}
We provide a systematic method to evaluate the potential threat that IDN homographs present.
Our data shows that there are more than a thousand IDN homographs in the \textit{.com} zone.
Even if the vast majority these are parking domains, there are no guarantees that they will remain inactive in the future.
Surprisingly, most TLDs do not have common policies to prevent the registration of homograph domains.

It is also important to remember that while the easiest solution would be displaying always URLs in Punycode instead of Unicode, that would completely defeat the purpose of IDNs.
Browsers have to balance user experience and security.
They need to allow users to type, navigate and see domains in their language of choice; while at the same time they should avoid misleading users into thinking they are in a legitimate domain when they are not.

Regarding future work, the next logical steps would be to repeat this analysis in other TLDs, and to improve the homograph matching algorithm.
A more challenging enchancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.
